Left-linear rules in adhesive categories

### 2024-02-13 icalp/fusione.tex
typos

%\rem{Non introdurrei una classe, come detto sopra}{
\begin{definition}[Strong Enforcing rewriting systems]A left-linear DPO rewriting system is \emph{strong enforcing} if every independence pair between two direct derivations is strong.
\end{definition}

@@

  As a consequence, $\der{D}$ and $\der{D}'$ are switch equivalent, but
  this is not acceptable when viewing equivalence classes of
  derivations as concurrent computations: in $\der{D}$ the first two
  steps are not sequential independent, while in $\der{D}'$ they are,
  intuitively because in $\der{D}$ rule $\rho_1$ uses the node
  generated by $\rho_0$, while in $\der{D}'$ rule $\rho_1$ uses the
  node which was in the initial graph. From the technical point of
  view, the property of being switch equivalent is not closed by
  prefix, something which prevents to derive a sensible concurrent
  sematics: if we limit to the first two steps, derivations
  $\der{D}_0; \der{D}_1$ and $\der{D}_0'; \der{D}_1'$ are not switch
  equivalent while $\der{D}$ and $\der{D}'$ would be
\end{example}

>>>>

%\rem{Non introdurrei una classe, come detto sopra}{
\begin{definition}[Strong Enforcing rewriting systems]A left-linear DPO rewriting system is \emph{strong enforcing} if every independence pair between two direct derivations is strong. }
\end{definition}

@@

  As a consequence, $\der{D}$ and $\der{D}'$ are switch equivalent, but
  this is not acceptable when viewing equivalence classes of
  derivations as concurrent computations: in $\der{D}$ the first two
  steps are not sequential independent, while in $\der{D}'$ they are,
  intuitively because in $\der{D}$ rule $\rho_1$ uses the node
  generated by $\rho_0$, while in $\der{D}'$ rule $\rho_1$ uses the
  node which was in the initial graph. From the technical point of
  view, the property of being switch equivalent is not closed by
  prefix, something which prevents to derive a sensible concurrent
  sematics: if we limit to the first two steps, derivations
  $\dder{D}_0; \dder{D}_1$ and $\dder{D}_0'; \dder{D}_1'$ are not switch
  equivalent while $\der{D}$ and $\der{D}'$ would be
\end{example}
